%hello
%please do the todos
\documentclass[11pt]{article}
%\usepackage{changepage}
%\usepackage{lipsum} % just for the example
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{mathpazo}
\usepackage{enumitem}
\usepackage[normalem]{ulem}
\usetikzlibrary{shapes, arrows}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\usepackage{amsmath}
\usepackage{graphicx}
\title{
GSPaid: Simple usecases
}
\author{سید محمد‌امین خدائی، علی عسگری، وحید بالازاده مرشت}
\begin{document}
\maketitle
\section{Contact admin}
\begin{itemize}
\item
Use Case: Contact admin
\item
Primary Actor: Anonymous User
\item
Scope: Administration System
\item
Level: User goal
\item
Brief: User fills a form of his name, email and massage and submit it so that it is delivered system admin
\item
Stakeholders:
\begin{itemize}
\item
Anonymous user: he wants his massages to be sent to the system admin
\end{itemize}
\item
Success Guarantees: user massage with his name and email addressed is delivered to admin
\item
Triggers:
User opens contact us page.
\end{itemize}

\subsection{Basic flow}
\begin{enumerate}
\item
System shows contact us form.
\item
User fills all fields of form with a correct email address format, and clicks on submit button.
\item
System shows a success label which means the massage has been sent.
\end{enumerate}

\subsection{Extensions}
2-3.a:
\begin{enumerate}
\item
User fills fields of form incompeletly or the email address with a wrong format, and clicks on submit.
\item
System shows a label meaning wrong input.
\end{enumerate}


\section{Sign Up}
\begin{itemize}
\item
Use Case: Sign Up
\item
Primary Actor: Anonymous User
\item
Scope: Authorization System
\item
Level: User goal
\item
Brief: User fills a form of his first name, last name, username, phone number, email, password and password confirmation and tries to create new account for himself.
\item
Stakeholders:
\begin{itemize}
\item
Anonymous user: he wants to create a new account with data he gives
\end{itemize}
\item
\item
Success Guarantees: System creates new user with data given.
\item
Triggers:
User opens Sign up page.
\end{itemize}
\subsection{Basic flow}
\begin{enumerate}
\item
System shows Sign up form.
\item
User fills all fields of form with correct email address format, password format, username format, same passwords, and new username and submits.
\item
System shows that new user with given data has been created
\end{enumerate}

\subsection{Extensions}
2-3
\begin{enumerate}[label=(\alph*)]
\item
\begin{enumerate}[label=(\arabic*)]
\item
User fills fields of form incompeletly and submits
\item
System shows a label meaning incomplete data.
\end{enumerate}

\item
\begin{enumerate}[label=(\arabic*)]
\item
User fills fields of form completely with incorrect input formats and submits
\item
System shows a label meaning correct format of each field with format condition beside it.
\end{enumerate}

\item
\begin{enumerate}[label=(\arabic*)]
\item
User fills fields of form completely with incorrect input formats and submits
\item
System shows a label meaning correct format of each field with format condition beside it.
\end{enumerate}

\item
\begin{enumerate}[label=(\arabic*)]
\item
User fills fields of form completely with correct input formats and taken username and submits
\item
System shows a label meaning that username is already taken.
\end{enumerate}
\end{enumerate}


\end{document}